Probing the inner kpc of massive lens galaxies with ALMA: Can the central images of strong lenses be detected?

### 2014-10-23 ms.tex
caption for figure 2

>>>>

\begin{figure}
\begin{center}
\centering
\includegraphics[trim= 0 0 0 0, width=0.48\textwidth]{figures/f_02.eps}
\centering
\end{center}
\caption{ Significance of detection of the central image as a function of the stellar core size. The colors correspond to different slopes of the stellar component. The solid curves correspond to a case without a SMBH while the dashed line show the result of a simulation which includes a $2\times10^8M_{\odot}$ SMBH at its center.
\label{f:f2}}
\end{figure}
